ArborVote -- Deliberative Decision-Making using Argument Trees \deleted[comment={Discuss multiple ways of determining the impact}]{and Rating Markets}

### 2024-11-15 Paper.tex
Apply fixes

\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}
\SetWatermarkColor[gray]{0.75}

@@

% Impact signal
The amount of approval and disapproval shares $n^\Y$ and $n^\N$ in the \ac{AMM}
signals the impact as a scalar value between $-1$ and $+1$
\begin{equation}
	\imp = 1-2\,\frac{n^\Y}{n^\Y+n^\N},
\end{equation}
where the fraction corresponds to the relative share of $\Y$ tokens available at the market.
Accordingly, the less approval shares $n^\Y$ are available at the market, the higher the impact $\imp$.
Arguments with negative impact values (in other words bad arguments) are not considered in the tallying phase later.

@@

% Design Rational
In summary, these mechanics incentivize, both, the debaters and voters, to consider and multiple arguments and perspectives.

@@

% Tallying
In the subsequent tallying phase,
the impact value $\imp$ determined by the markets is tallied up,
which is described in the following section.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Rating Markets}\label{sec:RatingMarkets}
An \ac{AMM}, more specifically a \ac{CPMM}, is used to provide liquidity for the rating markets.
The argument creator deposits $n^\T$ debate tokens 
to mint 
$n^\Y$ approval ($\Y$) and 
$n^\N$ disapproval ($\N$) shares
%at a price ratio
%\begin{equation}
%	\label{eq:PriceRatio}
%	p = \frac{n^\Y}{n^\N}
%\end{equation}
so that
\begin{equation}
	n^\Y+n^\N = \liq.
\end{equation}
The $\Y$ and $\N$ tokens form a trading pair
whose product has to remain constant
\begin{equation}
	k = n^\Y\cdot n^\N.
\end{equation}

>>>>

%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{1}
%\SetWatermarkColor[gray]{0.75}

@@

% Impact signal
The amount of approval and disapproval shares $n^\Y$ and $n^\N$ in the \ac{AMM}
signals the impact as a scalar value between $0$ and $1$
\begin{equation}
	\imp = 2\,\frac{n^\N}{n^\Y+n^\N}-1,
\end{equation}
where the fraction corresponds to the relative share of $\N$ tokens available at the market.
Accordingly, the less approval shares $n^\Y$ are available at the market, the higher the impact $\imp$.
Arguments with negative impact values (in other words bad arguments) are not considered in the tallying phase later.

@@

% Design Rational
In summary, these mechanics incentivize, both, the debaters and voters, to consider multiple arguments and perspectives.

@@

% Tallying
%In the subsequent tallying phase,
%the impact value $\imp$ determined by the markets is tallied up,
%which is described in the following section.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Rating Markets}\label{sec:RatingMarkets}
An \ac{AMM}, more specifically a \ac{CPMM}, is used to provide liquidity for the rating markets.
The argument creator deposits $n^\T$ debate tokens 
to mint 
$n^\Y$ approval ($\Y$) and 
$n^\N$ disapproval ($\N$) shares
%at a price ratio
%\begin{equation}
%	\label{eq:PriceRatio}
%	p = \frac{n^\Y}{n^\N}
%\end{equation}
so that
\begin{equation}
	n^\Y+n^\N = \liq.
\end{equation}
The $\Y$ and $\N$ tokens form a trading pair
whose product has to remain constant
\begin{equation}
	k = n^\Y\cdot n^\N.
\end{equation}
